EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-18 draft.tex
A few corrections

\begin{lstlisting}[language=Python, caption=Fragment of output message, label=code:result ]
{
"time_stamp": 1588455316.698875,
"evals": [
  {
    "gen_num": 0, "best_fitness": -259.96925945939404,
    "best_solution": [ -4.9446848321611405, 
                        2.593007989886873, 
                        2.0011025031167673],
    "num_of_evals": 17
  },
  {
    "gen_num": 49, "best_fitness": -419.47555780783347,
    "best_solution": [ -0.9165294450108963, 
                        2.291966676472422, 
                        1.8527006568795485],
    "num_of_evals": 28
  }
],
"worker_id": "4f5eb12e-8278-40de-b0f3-4ac18171566d",
"message_counter": 1,
"message_id": "cbcd2e82-e232-4818-8aec-2cd072c7cfe9",
"best_score": -419.47555780783347
}
\end{lstlisting}

@@

\begin{figure}[h!tbp]
  \centering
  \includegraphics[width=\textwidth]{aws}
  \caption{Boxplot of the number of evaluations per second, for 15 instances of function $f_4$,
   with three execution environments Local, Single task and Multi-task.
   }
  \label{fig:aws-results}
\end{figure}
%
\begin{table}[h!tbp]
  \small
  \caption{ Median number of the evaluations per second, for 15 instances of function $f_4$,
  with three execution environments Local, Single task and Multi task. The best result is shown in {\bf boldface}.}
  \label{tab:aws}
  \vspace{0.25cm}
  \centering

@@

\begin{table}[h!tbp]
  \small
  \caption{Speedup achieved with incrementing the number of workers for
    each dimension showing the p-rate for the Wilcoxon test.}
  % Say what highlights mean - JJ
  \label{tab:speedup:test}
  \vspace{0.25cm}
  \centering
  \begin{tabular}{lllllll}
            &               &               & \multicolumn{2}{l}{5 Populations} & \multicolumn{2}{l}{10 Populations} \\
  Dimension & \multicolumn{2}{l}{Increment} & Speedup         & p-value         & Speedup          & p-value         \\
  2         & 1w            & 2w            & {\ul 1.94}            & 6E-16           & 1.84             & 2E-16           \\
            & 2w            & 4w            & 1.61            & 2E-15           & 1.83             & 1E-15           \\
            & 4w            & 8w            & 1.24            & 1E-06           & 1.77             & 2E-16           \\
  3         & 1w            & 2w            & {\ul 1.93}            & 2E-16           & 1.90             & 2E-16           \\
            & 2w            & 4w            & 1.44            & 8E-15           & 1.71             & 2E-16           \\
            & 4w            & 8w            & 1.14            & 3E-05           & 1.83             & 2E-16           \\
  5         & 1w            & 2w            & 1.91            & 9E-16           & 1.91             & 2E-16           \\
            & 2w            & 4w            & 1.52            & 3E-11           & 1.82             & 2E-16           \\
            & 4w            & 8w            & 1.06            & 5E-03           & 1.77             & 2E-16           \\
  10        & 1w            & 2w            & 1.92            & 3E-16           & 1.90             & 2E-16           \\
            & 2w            & 4w            & 1.58            & 3E-16           & 1.89             & 2E-16           \\
            & 4w            & 8w            & {\ul 1.09}      & 1E-03           & 1.78             & 2E-16           \\
  20        & 1w            & 2w            & 1.91            & 2E-16           & 1.89             & 2E-16           \\
            & 2w            & 4w            & 1.64            & 2E-15           & 1.97             & 2E-16           \\
            & 4w            & 8w            & {\ul 1.04 }     & 1E-02           & 1.80             & 2E-16           \\
  40        & 1w            & 2w            & \textbf{2.00}   & 2E-16           & 1.95             & 2E-16           \\
            & 2w            & 4w            & 1.46            & 1E-09           & 1.95             & 2E-16           \\
            & 4w            & 8w            & {\ul 1.07}            & 3E-02           & \textbf{1.98}    & 2E-16          
  \end{tabular}
  \end{table}
%
Table~\ref{tab:speedup-table} shows the speedup obtained against the baseline of
one worker. When using eight workers, we achieved the maximum speed up for five
and ten populations, but interestingly, it was in dimension 40 and dimension 2 
(these values are shown in bold in the table).

Table~\ref{tab:speedup:test} shows the speedup obtained taking as the baseline
the previous configuration, for example, when increasing from four to eight
workers, and the p-rate for the left-tailed Wilcoxon test. There was an
increment in all cases, but again, for smaller dimensions, five populations with
fewer workers is a better option (see values underlined in the table) with the
best speedup, achieved for 40 dimensions, shown in bold. The worst speed was
going from four to eight workers at higher dimensions (underlined in the table).
For ten populations, adding more workers resulted in a linear speedup, but the
best speedup is obtained when increasing from four to eight workers at 40
dimensions (shown in bold).

>>>>

\begin{lstlisting}[language=Python, caption=Fragment of an output message, label=code:result ]
{
"time_stamp": 1588455316.698875,
"evals": [
  {
    "gen_num": 0, "best_fitness": -259.96925945939404,
    "best_solution": [ -4.9446848321611405, 
                        2.593007989886873, 
                        2.0011025031167673],
    "num_of_evals": 17
  },
  {
    "gen_num": 49, "best_fitness": -419.47555780783347,
    "best_solution": [ -0.9165294450108963, 
                        2.291966676472422, 
                        1.8527006568795485],
    "num_of_evals": 28
  }
],
"worker_id": "4f5eb12e-8278-40de-b0f3-4ac18171566d",
"message_counter": 1,
"message_id": "cbcd2e82-e232-4818-8aec-2cd072c7cfe9",
"best_score": -419.47555780783347
}
\end{lstlisting}

@@

\begin{figure}[h!tbp]
  \centering
  \includegraphics[width=\textwidth]{aws}
  \caption{Boxplot of the number of evaluations per second, for 15 instances of function $f_4$,
   with three execution environments Local, Single task, and Multi-task.
   }
  \label{fig:aws-results}
\end{figure}
%
\begin{table}[h!tbp]
  \small
  \caption{ Median number of the evaluations per second, for 15 instances of function $f_4$,
  with three execution environments Local, Single task, and Multi task. The best result is shown in {\bf boldface}.}
  \label{tab:aws}
  \vspace{0.25cm}
  \centering

@@

\begin{table}[h!tbp]
  \small
  \caption{Speedup achieved with incrementing the number of workers for
    each dimension showing the p-value for the Wilcoxon test. Best and Worst are highlighted (bold and underlined) }
  % Say what highlights mean - JJ
  \label{tab:speedup:test}
  \vspace{0.25cm}
  \centering
  \begin{tabular}{lllllll}
            &               &               & \multicolumn{2}{l}{5 Populations} & \multicolumn{2}{l}{10 Populations} \\
  Dimension & \multicolumn{2}{l}{Increment} & Speedup         & p-value         & Speedup          & p-value         \\
  2         & 1w            & 2w            & {\ul 1.94}            & 6E-16           & 1.84             & 2E-16           \\
            & 2w            & 4w            & 1.61            & 2E-15           & 1.83             & 1E-15           \\
            & 4w            & 8w            & 1.24            & 1E-06           & 1.77             & 2E-16           \\
  3         & 1w            & 2w            & {\ul 1.93}            & 2E-16           & 1.90             & 2E-16           \\
            & 2w            & 4w            & 1.44            & 8E-15           & 1.71             & 2E-16           \\
            & 4w            & 8w            & 1.14            & 3E-05           & 1.83             & 2E-16           \\
  5         & 1w            & 2w            & 1.91            & 9E-16           & 1.91             & 2E-16           \\
            & 2w            & 4w            & 1.52            & 3E-11           & 1.82             & 2E-16           \\
            & 4w            & 8w            & 1.06            & 5E-03           & 1.77             & 2E-16           \\
  10        & 1w            & 2w            & 1.92            & 3E-16           & 1.90             & 2E-16           \\
            & 2w            & 4w            & 1.58            & 3E-16           & 1.89             & 2E-16           \\
            & 4w            & 8w            & {\ul 1.09}      & 1E-03           & 1.78             & 2E-16           \\
  20        & 1w            & 2w            & 1.91            & 2E-16           & 1.89             & 2E-16           \\
            & 2w            & 4w            & 1.64            & 2E-15           & 1.97             & 2E-16           \\
            & 4w            & 8w            & {\ul 1.04 }     & 1E-02           & 1.80             & 2E-16           \\
  40        & 1w            & 2w            & \textbf{2.00}   & 2E-16           & 1.95             & 2E-16           \\
            & 2w            & 4w            & 1.46            & 1E-09           & 1.95             & 2E-16           \\
            & 4w            & 8w            & {\ul 1.07}            & 3E-02           & \textbf{1.98}    & 2E-16          
  \end{tabular}
  \end{table}
%
Table~\ref{tab:speedup-table} shows the speedup obtained against the baseline of
one worker. When using eight workers, we achieved the maximum speed up for five
and ten populations, but interestingly, it was in dimension 40 and dimension 2 
(these values are shown in bold in the table).

Table~\ref{tab:speedup:test} shows the speedup obtained taking as the baseline
the previous configuration, for example, when increasing from four to eight
workers, and the p-value for the left-tailed Wilcoxon test. There was an
increment in all cases, but again, for smaller dimensions, five populations with
fewer workers is a better option (see values underlined in the table) with the
best speedup, achieved for 40 dimensions, shown in bold. The worst speed was
going from four to eight workers at higher dimensions (underlined in the table).
For ten populations, adding more workers resulted in a linear speedup, but the
best speedup is obtained when increasing from four to eight workers at 40
dimensions (shown in bold).
